M.Sc. Proposal: \\ \bigskip Computational Electrokinetics

### 2012-12-19 notes/thesis-latex-template/thesis.tex
Add sample solver code

@@

\subsection{Operator Interface}
The base \verb|Operator| interface is defined by 
supporting the computation of a residual vector \verb|Operator::res()|
and a gradient matrix \verb|Operator::grad()|, given an input vector $\bx$.
This interface is implemented by specific operator classes,
which are used to construct the system operator $\cO$, so that 
the Newton solver (that requires computing the residual and the gradient) 
can be applied automatically.
Each such operator may have other operators as its inputs, so the residual
and the gradient are computed recursively, using the chain rule (applied to operators).

@@

\subsection{Handling the Singularity} \label{sec:singular}
The electric potential $\varPhi$ (in electrophoresis case) and the pressure $P$ (in both cases) 
are defined up to an additive constant, since the system equations and the boundary conditions
contain only their derivatives.
In order to overcome the singularity of the linear system 
$\bG \Delta\bx = -\br$, we set the variable at 
a specific grid point to be $0$.
In order to retain square system, we should remove one conservation equation at this grid point too.
In the case of pressure $P$, we remove one mass conservation equation,
$\bnabla \cdot \bV = 0$, at this grid point. 
In the case of electric potential, we remove the charge conservation
equation, $\bnabla \cdot \pars{C \bnabla \varPhi} = 0$, at this grid point.
For $\br = \cO(\bx)$ and $\bG = \bnabla \cO(\bx)$, the new square linear system reads:
\begin{equation}
\mathbb{R} \bG \mathbb{P} \cdot \delta\bx = -\mathbb{R} \br,
\end{equation}
where $\mathbb{P}$ matrix is used to remove the columns
and $\mathbb{R}$ matrix is used to remove the rows of $\bG$,
where the update step is $\Delta \bx = \mathbb{P} \cdot \delta \bx$.

@@

\subsection{Sample source code}

\subsubsection{Variable class}
\begin{figure}
\begin{lstlisting}
classdef Variable < handle
properties
    value;
end

methods
    function self = Variable(varargin)
        self.value = col(varargin{:});
    end

    function r = res(self)
        r = self.value(:);
    end

    function G = grad(self) 
        G = speye(numel(self.value));
    end

    function update(self, delta)
        assert(numel(self.value) == numel(delta))
        self.value = self.value + delta;
    end
end

end
\end{lstlisting}
\end{figure}

\subsubsection{Operator interface}
\begin{lstlisting}
% An operator base class.
classdef Operator < handle
properties
    grid; % a grid object for the output
end
methods
    function op = Operator(grid)
        op.grid = grid;
    end
    function op = plus(op1, op2)
        op = Sum(op1, op2);
    end
    function op = minus(op1, op2)
        op = Minus(op1, op2);
    end
    function op = uminus(op)
        op = Product(-1, op);
    end
    function op = mtimes(op1, op2)
        op = Product(op1, op2);
    end
    function op = log(op)
        op = Func(op, 'log(x)');
    end
    function op = exp(op)
        op = Func(op, 'exp(x)');
    end
    function op = sinh(op)
        op = Func(op, 'sinh(x)');
    end
    function op = cosh(op)
        op = Func(op, 'cosh(x)');
    end
    function op = tanh(op)
        op = Func(op, 'tanh(x)');
    end
end
end
\end{lstlisting}

\subsubsection{Linear operators}
\begin{lstlisting}
% Linear Sparse operator.
classdef Linear < Operator
properties
    L;
    op;
end

methods
    function self = Linear(grid, op, L)
        self = self@Operator(grid);
        self.op = op;
        if (nargin < 3 || isempty(L))
            L = 1;
        end
        if isequal(L, 1)
            L = speye(grid.numel); % Default copy operator
        end
        assert(size(L, 1) == grid.numel);
        assert(size(L, 2) == op.grid.numel);
        self.L = L;
    end
    function r = res(self)
        r = self.L * self.op.res();
    end
    function G = grad(self)
        G = dot_prod(self.L, self.op.grad());
    end
end

end
\end{lstlisting}

\begin{lstlisting}
classdef Deriv < Linear

methods
    function self = Deriv(grid, op, dim)
        dir = (1:2) == dim;
        assert(any(dir));

        J = true(op.grid.size);
        J1 = shift(J, dir); % forward mask
        J0 = shift(J1, -dir); % backward mask
        J = [find(J0(:)) find(J1(:))]; % column indices

        N = size(J, 1); % # of equations
        M = op.grid.numel; % # of variables
        I = repmat(1:N, 1, 2); % row indices

        % Finite difference operator
        D = sparse(I, J, repmat([-1 1], N, 1), N, M);

        switch dim % Choose coordinate
            case 1, x = op.grid.R;
            case 2, x = op.grid.T;
        end

        % L = D/Dx
        Dx = D * x(:);
        assert(all(Dx));

        L = spdiag( 1./Dx ) * D;
        self = self@Linear(grid, op, L);        
    end
end

end
\end{lstlisting}

\begin{lstlisting}
classdef Interp < Linear

methods
    function self = Interp(grid, op)
        L = interpolate_grids(grid, op.grid);
        self = self@Linear(grid, op, L);
    end
end

end

function S = interpolate_grids(dst, src)
    n = fieldnames(src);
    S1 = interpolate_matrix(src.(n{1}), dst.(n{1}));
    S1 = kron(speye(numel(src.(n{2}))), S1); % Interpolate on 1st dimension
    S2 = interpolate_matrix(src.(n{2}), dst.(n{2}));
    S2 = kron(S2, speye(numel(dst.(n{1})))); % Interpolate on 2nd dimension
    S = S2 * S1;    
end

function S = interpolate_matrix(x, xi)
    x = x(:);
    xi = xi(:);
    N = numel(xi);
    L = zeros(N, 1);
    R = zeros(N, 1);
    for k = 1:N
        less = x <= xi(k);
        more = x >= xi(k);
        if any(less)
            L(k) = find(less, 1, 'last');
        end
        if any(more)
            R(k) = find(more, 1, 'first');
        end
    end
    u = L & R; % valid interpolatory points
    I = find(u);
    L = L(u);
    R = R(u);
    xi = xi(u);

    I = [I I];
    J = [L R];
    dx = x(R) - x(L);
    V = [(x(R)-xi), (xi-x(L))];
    V(dx>0, :) = spdiag( 1./dx(dx>0) ) * V(dx>0, :);
    V(~dx, :) = 1/2;
    S = sparse(I, J, V, N, numel(x));
end
\end{lstlisting}

\subsubsection{Binary Operators}
\begin{lstlisting}
% Abstract class for a binary operator
classdef Binary < Operator
properties
    op1, op2;
end

methods
    function self = Binary(op1, op2)
        if isa(op1, 'Operator') && isa(op2, 'Operator')
            assert(op1.grid == op2.grid);
        end
        if ~isa(op1, 'Operator')
            op1 = Const(op2.grid, op1);
        end
        if ~isa(op2, 'Operator')
            op2 = Const(op1.grid, op2);
        end
        self = self@Operator(op1.grid);
        self.op1 = op1;
        self.op2 = op2;
    end
end

end
\end{lstlisting}
\begin{lstlisting}
classdef Product < Binary

methods
    function self = Product(op1, op2)
        self = self@Binary(op1, op2);
    end
    function r = res(self)
        r = self.op1.res() .* self.op2.res();
    end
    function g = grad(self)
        g1 = dot_prod(spdiag(self.op2.res()), self.op1.grad());
        g2 = dot_prod(spdiag(self.op1.res()), self.op2.grad());
        g = g1 + g2;
    end
end

end
\end{lstlisting}

\begin{lstlisting}
classdef Sum < Binary

methods
    function self = Sum(op1, op2)
        self = self@Binary(op1, op2);
    end
    function r = res(self)
        r = self.op1.res() + self.op2.res();
    end
    function g = grad(self)
        g1 = self.op1.grad();
        g2 = self.op2.grad();
        g = g1 + g2;
    end
end

end
\end{lstlisting}

\subsubsection{Unary operator}
\begin{lstlisting}
classdef Func < Operator
properties
    op; % Input operator
    func; % y = f(x)
    deriv; % dy/dx = f'(x)
end

methods
    function self = Func(op, func)
        grid = op.grid; % Reuse operator's grid
        self = self@Operator(grid);
        self.op = op;
        if ~isempty(func)
            if isa(func, 'char')
                func = sym(func);
            end % using symoblic toolbox
            self.func = matlabFunction(func);
            self.deriv = matlabFunction(diff(func));
        else % just copy values to grid
            self.func = @(x) x;
            self.deriv = @(x) ones(size(x));
        end
    end
    function r = res(self)
        r = self.func( self.op.res() );
    end
    function G = grad(self)
        r = self.op.res();
        G = dot_prod(spdiag( self.deriv(r) ), self.op.grad());
    end
end

end
\end{lstlisting}

\begin{lstlisting}
classdef Const < Operator
properties
    val;
end

methods
    function self = Const(grid, val)
        self = self@Operator(grid);
        if isa(val, 'float')
            if numel(val) == 1
                val = repmat(val, grid.size);
            end
            self.val = val;
        else % function handle evaluated point-wise
            if isa(val, 'char')
                val = str2func(['@(r,t) ' val]);
            end
            self.val = arrayfun(val, grid.R, grid.T);
        end
    end
    function r = res(self)
        r = self.val(:);
    end
    function G = grad(self)
        G = sparse(0); % [0]
    end
end

end
\end{lstlisting}

\begin{lstlisting}
\end{lstlisting}

@@

\section{Asymptotic Analysis} \label{sec:asymp}
In order to validate the numerical results, an asymptotic analysis has been applied 
to the nonlinear systems of ion-exchanger migration 
and highly charged particle electrophoresis.
We present here the asymptotic analysis for the ion-exchanger case \cite{yariv2010migration},
and the asymptotic analysis for the electrophoresis case \cite{schnitzer2012surface}
is derived by Schnitzer and Yariv at \cite{schnitzer2012cubic}.

The derivation is performed as follows.
The nonlinear system (composed of the governing equations and the boundary conditions) 
is written as $\cO(\bx;\beta) = \bzero$.
For small $\beta$, the solution to the nonlinear system can be expanded in a Taylor series in $\beta$:
\begin{equation}
\bx = \bx(\beta) \approx \sum_n \bx_n \beta^n.
\end{equation}
The nonlinear terms
are expanded around $\beta = 0$:
\begin{equation}
\bzero = \cO(\bx) = \sum_i \cO_i(\bx_0, \ldots \bx_i) \beta^i.
\end{equation}

Thus, the $O(\beta^k)$ term $\bx_k$ can be found recursively by solving 
$\cO_k(\bx_0, \bx_1, \ldots, \bx_k) = \bzero$,
given the previous solutions for $\bx_0, \ldots, \bx_{k-1}$.
The derivation is validated using MATLAB symbolic toolbox by the code 
at \verb|symbolic/asymp.m| \cite{source}.

@@

For $\beta = 0$ (no electric field is applied), the steady-state solution is $\cU = 0$:
\begin{equation}\begin{array}{cccc}
\varPhi_0(r,\theta) = 0, &
C_0(r,\theta) = 1, &
\bV_0(r,\theta) = \bzero, &
P_0(r,\theta) = 0.
\end{array}\end{equation}

Assuming $\beta \ll 1$, the linearized equations and boundary conditions are
\begin{equation} \begin{array}{ccc}
\Laplacian \varPhi_1 = 0, &
\Laplacian C_1 = 0, &
\bLaplacian \bV_1 - \bnabla P_1 = \bzero.
\end{array}\end{equation}

The first-order terms $\bx_1$ are given by (see \cite{yariv2010migration} for full derivation)
\begin{equation} \begin{array}{cccc}
\varPhi_1 = \pars{\frac{1}{4r^2} - r}\cos\theta, &
C_1 = \frac{3}{4r^2} \cos\theta, &
\Psi_1 = \cU_1 \pars{\frac{1}{r} - r^2} \frac{\sin^2\theta}{2}, &
P_1 = 0,
\end{array} \end{equation}
and the linear velocity term is:
\begin{equation} \label{eq:linear_velocity}
\cU_1(\gamma) = 2 \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}.
\end{equation}
For $\gamma > 1$, the Debye layer has a positive space charge, 
corresponding to a negative particle charge -- 
yielding negative drift velocity, $\cU < 0$. 
For $\gamma < 1$, we have $\cU > 0$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Third-Order (cubic in $\beta$) Solution} \label{app:cubic}
Note that, due to symmetry considerations, $\cU(\beta)$ is an anti-symmetric function.
Therefore, $\cU_2 = 0$ and the next velocity term is the cubic one:
\begin{equation} \label{eq:cubic}
\cU(\beta) \approx \beta \cU_1 + \beta^3 \cU_3 + O(\beta^5).
\end{equation}

The cubic terms $\bx_3$ are computed by solving a linear PDE system 
with a right-hand side determined by the linear terms $\bx_1$ and the quadratic terms $\bx_2$.

>>>>

\setlength{\textheight}{9in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{0.05in}
\setlength{\headheight}{0.2in}
\setlength{\headsep}{0.1in}
\setlength{\evensidemargin}{0in}
\setlength{\oddsidemargin}{0in}
\setlength{\parindent}{0.0 in}
\setlength{\parskip}{0.1 in}

@@

\subsection{Operator Interface} \label{sec:operator-interface}
The base \verb|Operator| interface is defined by 
supporting the computation of a residual vector \verb|Operator::res()|
and a gradient matrix \verb|Operator::grad()|, given an input vector $\bx$.
This interface is implemented by specific operator classes,
which are used to construct the system operator $\cO$, so that 
the Newton solver (that requires computing the residual and the gradient) 
can be applied automatically.
Each such operator may have other operators as its inputs, so the residual
and the gradient are computed recursively, using the chain rule (applied to operators).

@@

\subsection{Handling the Singularity} \label{sec:singular}
The electric potential $\varPhi$ (in electrophoresis case) and the pressure $P$ (in both cases) 
are defined up to an additive constant, since the system equations and the boundary conditions
contain only their derivatives.
In order to overcome the singularity of the linear system 
$\bG \Delta\bx = -\br$, we set the variable at 
a specific grid point to be $0$.
In order to retain a square system, we remove one conservation equation at this grid point too.
In the case of pressure $P$, we remove one mass conservation equation,
$\bnabla \cdot \bV = 0$, at this grid point. 
In the case of electric potential, we remove the charge conservation
equation, $\bnabla \cdot \pars{C \bnabla \varPhi} = 0$, at this grid point.
For $\br = \cO(\bx)$ and $\bG = \bnabla \cO(\bx)$, the new square linear system reads:
\begin{equation}
\mathbb{R} \bG \mathbb{P} \cdot \delta\bx = -\mathbb{R} \br,
\end{equation}
where $\mathbb{P}$ matrix is used to remove the columns
and $\mathbb{R}$ matrix is used to remove the rows of $\bG$,
where the update step is $\Delta \bx = \mathbb{P} \cdot \delta \bx$.

@@

\section{Source code overview}

\subsection{Variable}
We define the variable vector $\bx$ as \verb|Variable| 
operator using the following MATLAB code:

\begin{lstlisting}
classdef Variable < handle
properties
    value;
end
methods
    function self = Variable(varargin)
        self.value = col(varargin{:});
    end
    function r = res(self)
        r = self.value(:);
    end
    function G = grad(self) 
        G = speye(numel(self.value));
    end
    function update(self, dv)
        self.value = self.value + dv;
    end
end
\end{lstlisting}
Then the initial solution for the solver is set using
$\bx = \verb|Variable|(\varPhi, C, V_r, V_t, P)$
from the initial conditions of the solver.

\subsection{Grid}
Most of the operators are defined a \verb|Grid| object,
enabling validation of operators compatibility and 
convenient interpolation between grids. Note that
each operator must define its \verb|res()| and \verb|grad()|
functions, for residual and gradient computation, respectively.
\begin{lstlisting}
% Regular structured grid class
classdef Grid < handle
properties
    x, y;
    X, Y;
    size;    
    numel;
end
methods
    function self = Grid(x, y)
        self.x = x(:);
        self.y = y(:);
        [self.X, self.Y] = ndgrid(self.x, self.y);
        self.size = [numel(self.x), numel(self.y)];
        self.numel = prod(self.size);
    end
end
\end{lstlisting}
\begin{lstlisting}
classdef Operator < handle
properties
    grid; % a grid object for the output
end
methods
    function op = Operator(grid)
        op.grid = grid;
    end
    function op = plus(op1, op2)
        op = Sum(op1, op2);
    end
    function op = minus(op1, op2)
        op = Minus(op1, op2);
    end
    function op = uminus(op)
        op = Product(-1, op);
    end
    function op = mtimes(op1, op2)
        op = Product(op1, op2);
    end
    function op = log(op)
        op = Func(op, 'log(x)');
    end
    function op = exp(op)
        op = Func(op, 'exp(x)');
    end
    function op = sinh(op)
        op = Func(op, 'sinh(x)');
    end
    function op = cosh(op)
        op = Func(op, 'cosh(x)');
    end
    function op = tanh(op)
        op = Func(op, 'tanh(x)');
    end
end
\end{lstlisting}
Thus, various computations can be applied on simple operators, 
creating more complex operators, such as
\verb|op4 = op1 * exp(op2 + tanh(op3))|. 
Since each operator can compute its residual and gradient, we
can compute automatically the residual and gradient of \verb|o4|
from these of \verb|o1|, \verb|o2|, \verb|o3| using the derivation
rules described at \ref{sec:operator-interface}.

\subsection{Operators}
An operator can be created with $n$ existing operators as input.
\verb|Const| is an operator that corresponds to $n=0$, whose 
residual value is constant and gradient matrix is zero.

\begin{lstlisting}
classdef Const < Operator
properties
    val;
end
methods
    function self = Const(grid, val)
        self = self@Operator(grid);
        if isa(val, 'float')
            if numel(val) == 1
                val = repmat(val, grid.size);
            end
            self.val = val;
        else % function handle evaluated point-wise
            if isa(val, 'char')
                val = str2func(['@(r,t) ' val]);
            end
            self.val = arrayfun(val, grid.R, grid.T);
        end
    end
    function r = res(self)
        r = self.val(:);
    end
    function G = grad(self)
        G = sparse(0); % [0]
    end
end
\end{lstlisting}

\subsubsection{Unary operators}
Unary operators have one existing operator as input. 
\verb|Func| operator implements point-wise analytic function
application (whose derivative is computed using symbolic differentiation toolbox) on the same grid of the input operator. 
\verb|Linear| operator is implemented
using multiplication by a constant sparse matrix 
\verb|L|, which is also the gradient of the operator.
\begin{lstlisting}
classdef Func < Operator
properties
    op; % Input operator
    func; % y = f(x)
    deriv; % dy/dx = f'(x)
end
methods
    function self = Func(op, func)
        grid = op.grid; % Reuse operator's grid
        self = self@Operator(grid);
        self.op = op;
        if isa(func, 'char')
        	func = sym(func); 
        end 
        self.func = matlabFunction(func);
        self.deriv = matlabFunction(diff(func));
    end
    function r = res(self)
        r = self.func( self.op.res() );
    end
    function G = grad(self)
        r = self.op.res();
        G = spdiag( self.deriv(r) ) * self.op.grad();
    end
end
\end{lstlisting}
\begin{lstlisting}
classdef Linear < Operator
properties
    L;
    op;
end
methods
    function self = Linear(grid, op, L)
        self = self@Operator(grid);
        self.op = op;
        self.L = L;
    end
    function r = res(self)
        r = self.L * self.op.res();
    end
    function G = grad(self)
        G = self.L * self.op.grad();
    end
end
\end{lstlisting}
\verb|Deriv| and \verb|Interp| operators (implementing discrete
differentiation and grid interpolation) derive from \verb|Linear|
base class operator and specify \verb|L| sparse matrix accordingly.

\subsubsection{Binary operators}
Binary operators such as addition, subtraction and point-wise 
multiplication are implemented as operators whose
output grid is the as the grid of their inputs. 
The implementation is used by operator overloading in 
the base class \verb|Operator|.

\subsubsection{$N$-ary operators}
All equations and boundary condition operators are defined
as operators \verb|{op1, op2, ... opN}|. 
Then, they are combined using the $N$-ary operator 
\verb|op = Join(op1, op2, ... opN)|, creating
the system operator \verb|op|.

\begin{lstlisting}
classdef Join < handle
properties
    ops;
end
methods
    function self = Join(varargin)
        self.ops = varargin;
        for k = 1:numel(self.ops),
            op = self.ops{k};
        end
    end
    function r = res(self)
        r = cell(numel(self.ops), 1);
        for k = 1:numel(self.ops)
            r{k} = self.ops{k}.res();
        end
        r = cat(1, r{:});
    end
    function G = grad(self) 
        G = cell(numel(self.ops), 1);
        for k = 1:numel(self.ops)
            G{k} = self.ops{k}.grad();
        end
        G = cat(1, G{:});
    end
end
\end{lstlisting}

\subsection{Sample source code}
The following example shows how to define the following boundary-value problem:
\begin{align}
\Laplacian F(x,y) &= 1 & (x,y) &\in [0,1]^2 \\
F(0, y) = F(1, y) &= 0 & y &\in [0,1] \\
\deriv{F}{y}(x, 0) = \deriv{F}{y}(x, 1) &= 0 & x &\in [0,1]
\end{align}

\begin{lstlisting}
% Grid definition
x = linspace(0, 1);
y = linspace(0, 1);
g = Grid(x, y);
x_ = (x(1:end-1) + x(2:end)) * 0.5;
y_ = (y(1:end-1) + y(2:end)) * 0.5;
xi = x(2:end-1);
yi = y(2:end-1);
% Variable Definition
v = Variable(zeros(g.size));
F = Linear(g, v, speye(g.numel));
% Equations
Fx = Deriv(Grid(x_, y), F, 1);
Fy = Deriv(Grid(x, y_), F, 2);
Fxx = Deriv(Grid(xi, yi), Fx, 1);
Fyy = Deriv(Grid(xi, yi), Fy, 2);
eq = {(Fxx + Fyy) - Const(1)};             % Laplacian(F) = 1
% Boundary conditions
bnd = {Interp(Grid(x(1)  , y(2:end-1)), F); ... % F(0, y) = 0
	   Interp(Grid(x(end), y(2:end-1)), F); ... % F(1, y) = 0
       Interp(Grid(x, y_(1)  ), Fy); ...    % dF/dy(x, 0) = 0
       Interp(Grid(x, y_(end)), Fy)}		% dF/dy(x, 1) = 0
% System operator
ops = cat(1, eq, bnd)
op = Join(ops{:})
% Solve by Newton iteration
r = op.res()
G = op.grad()
v.update(-(G\r))
\end{lstlisting}

@@

\section{Asymptotic Analysis} \label{sec:asymp}
In order to validate the numerical results, an asymptotic analysis has been applied 
to the nonlinear systems of ion-exchanger migration 
and highly charged particle electrophoresis.
We present here the asymptotic analysis for the ion-exchanger case \cite{yariv2010migration},
while the asymptotic analysis for the electrophoresis case \cite{schnitzer2012surface}
is derived by Schnitzer and Yariv at \cite{schnitzer2012cubic}.

The derivation is performed as follows.
The nonlinear system (composed of the governing equations and the boundary conditions) 
is written as $\cO(\bx;\beta) = \bzero$.
For small $\beta$, the solution to the nonlinear system can be expanded in a Taylor series in $\beta$:
\begin{equation}
\bx = \bx(\beta) \approx \sum_n \bx_n \beta^n.
\end{equation}
The nonlinear terms
are expanded around $\beta = 0$:
\begin{equation}
\bzero = \cO(\bx) = \sum_i \cO_i(\bx_0, \ldots \bx_i) \beta^i.
\end{equation}
Thus, the $O(\beta^k)$ term $\bx_k$ can be found recursively by solving 
$\cO_k(\bx_0, \bx_1, \ldots, \bx_k) = \bzero$,
given the previous solutions for $\bx_0, \ldots, \bx_{k-1}$.
The derivation is validated using MATLAB symbolic toolbox by the code 
at \verb|symbolic/asymp.m| \cite{source}.

@@

For $\beta = 0$ (no electric field is applied), the steady-state solution is $\cU = 0$:
\begin{equation}\begin{array}{cccc}
\varPhi_0(r,\theta) = 0, &
C_0(r,\theta) = 1, &
\bV_0(r,\theta) = \bzero, &
P_0(r,\theta) = 0.
\end{array}\end{equation}
Assuming $\beta \ll 1$, the linearized equations and boundary conditions are
\begin{equation} \begin{array}{ccc}
\Laplacian \varPhi_1 = 0, &
\Laplacian C_1 = 0, &
\bLaplacian \bV_1 - \bnabla P_1 = \bzero.
\end{array}\end{equation}
The first-order terms $\bx_1$ are given by (see \cite{yariv2010migration} for full derivation)
\begin{equation} \begin{array}{cccc}
\varPhi_1 = \pars{\frac{1}{4r^2} - r}\cos\theta, &
C_1 = \frac{3}{4r^2} \cos\theta, &
\Psi_1 = \cU_1 \pars{\frac{1}{r} - r^2} \frac{\sin^2\theta}{2}, &
P_1 = 0,
\end{array} \end{equation}
and the linear velocity term is:
\begin{equation} \label{eq:linear_velocity}
\cU_1(\gamma) = 2 \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}.
\end{equation}
For $\gamma > 1$, the Debye layer has a positive space charge, 
corresponding to a negative particle charge -- 
yielding negative drift velocity, $\cU < 0$. 
For $\gamma < 1$, we have $\cU > 0$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Third-Order (cubic in $\beta$) Solution} \label{app:cubic}
Note that, due to symmetry considerations, $\cU(\beta)$ is an anti-symmetric function.
Therefore, $\cU_2 = 0$ and the next velocity term is the cubic one:
\begin{equation} \label{eq:cubic}
\cU(\beta) \approx \beta \cU_1 + \beta^3 \cU_3 + O(\beta^5).
\end{equation}
The cubic terms $\bx_3$ are computed by solving a linear PDE system 
with a right-hand side determined by the linear terms $\bx_1$ and the quadratic terms $\bx_2$.

\begin{align*}
\varPhi_3 &= \frac{15\cU_1\alpha + 6 }{64}\cos\theta  - \frac{3 \cU_1\alpha}{32} {\cos}^3\theta
 + \frac{183 {\cU_1}^2\alpha^2 - 839 \cU_1\alpha - 470}{2560 r^2} \cos\theta 
\\ \nonumber &
+ \frac{3 \cos\theta \left(5 \cU_1\alpha - 6 {\cos^2\theta} - 4 \cU_1\alpha {\cos^2\theta} + 4\right)}{64 r^3} + \frac{\left(2 \cU_1\alpha - 1\right) \left(\cos\theta - 3 {\cos}^3\theta\right)}{64 r^5} 
\\ &+ {{\cos}^3\theta \left(\frac{15 \cU_1\alpha}{64} + \frac{3}{32}\right)}{r^{-2}} 
- \left(3 \cos\theta - 5 {\cos}^3\theta\right) \left( - \frac{19 {\cU_1}^2\alpha^2}{5120} + \frac{97 \cU_1\alpha}{5120} + \frac{3 \cU_2\alpha}{320} + \frac{21}{1280}\right){r^{-4}} 
\\ \nonumber &
+ {{\cos}^3\theta \left(\frac{\cU_1\alpha}{64} + \frac{3}{64}\right)}{r^{-6}},
\end{align*}
\begin{align*}
C_3 &=
\frac{3 {{\cU_1}}^2\alpha^2 {\cos^3\theta}}{32} + \frac{\cos\theta \left(797 {{\cU_1}}^2\alpha^2 + 419 {\cU_1}\alpha - 512 {\cU_2}\alpha + 174\right)}{2560 r^2} 
- \frac{3 {\cU_1}\alpha \cos\theta \left(5 {\cU_1}\alpha + 2\right)}{64} 
\\ \nonumber &
- {\left(3 \cos\theta - 5 {\cos^3\theta}\right) \left(\frac{59 {{\cU_1}}^2\alpha^2}{5120} + \frac{103 {\cU_1}\alpha}{5120} + \frac{69 {\cU_2}\alpha}{320} + \frac{3}{1280}\right)}{r^{-4}} 
\\ \nonumber &
+ \frac{\alpha \left(\cos\theta - 3 {\cos^3\theta}\right) \left(5\alpha {{\cU_1}}^2 + 2 {\cU_1} + 16 {\cU_2}\right)}{128 r^5} 
\\ \nonumber &
- \frac{3\alpha \cos\theta \left( - 8\alpha {{\cU_1}}^2 {\cos^2\theta} + 7\alpha {{\cU_1}}^2 + 2 {\cU_1} + 32 {\cU_2} {\cos^2\theta} - 32 {\cU_2}\right)}{128 r^3} 
\\ \nonumber &
+ \frac{{{\cU_1}}^2\alpha^2 {\cos^3\theta}}{32 r^6} - \frac{3 {\cU_1}\alpha {\cos^3\theta} \left(5 {\cU_1}\alpha + 2\right)}{64 r^2},
\end{align*}
\begin{align*}
\Psi_3 &=
r^2 {\sin^2\theta} \left(\frac{{\cW_2}}{15} - \frac{{\cW_1}}{3} + \frac{209}{3360}\right) 
 - {{\sin^2\theta} \left(\frac{5 {\cW_2}}{3} - \frac{{\cW_1}}{3} + \frac{35}{264}\right)}{r^{-1}}
 + {{\sin^4\theta} \left(2 {\cW_2} + \frac{761}{5632}\right)}{r^{-1}} 
\\ \nonumber & 
- \frac{{\sin^2\theta} \left(1848 r^6 {\sin^2\theta} - 2079 r^3 {\sin^2\theta} + 924 r^3 - 7 {\sin^2\theta} + 10\right)}{19712 r^5} 
%\\ \nonumber & 
\frac{4 {\sin^2\theta} - 5 {\sin^4\theta}}{r^3} \\ & + \left(\frac{{\cU_1}\alpha}{16} - \frac{1}{8}\right) \frac{2 r^3 - 3 r^2 + 1}{4 r} {\sin^2\theta},
\end{align*}
\begin{align*}
\cW_1 &= \frac{69}{512 \left(\sqrt{\gamma} + 1\right)} - \frac{1407\alpha^2 {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^3}{1280} - \frac{123 \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{1280} - \frac{27}{512 {\left(\sqrt{\gamma} + 1\right)}^2} 
\\ & -\frac{1899\alpha {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^2}{2560} 
- \frac{\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right) \left(\frac{81}{16 \left(\sqrt{\gamma} + 1\right)} - \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right) \left(\frac{27\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{4} + \frac{27}{8}\right)\right)}{320} 
\\ & + \frac{21\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{128 \left(\sqrt{\gamma} + 1\right)},
\end{align*}
\begin{align*}
\cW_2 &= \frac{9 \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{256} 
+ \frac{21\alpha^2 {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^3 + 
15\alpha {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^2}{64} 
- \frac{27}{512 {\left(\sqrt{\gamma} + 1\right)}^2}
\\ \nonumber &
- \frac{297\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right) + 54}{1024 \left(\sqrt{\gamma} + 1\right)}.
\end{align*}
The cubic solution satisfies the boundary conditions only when $\alpha\cU_1 = 0$,
due to boundary conditions mismatch for $C$ at $r \rightarrow \infty$, when
the diffusion and the advection terms become of the same order of magnitude.
The cubic correction velocity terms (for $\alpha = 0$)
turn out to be:
\begin{equation}
\cU_3(\gamma) = \frac{31}{320(\sqrt\gamma + 1)} - \frac{9}{320(\sqrt\gamma + 1)^2} + \frac{1}{1680} - \frac{11}{160} \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}.
\end{equation}
The cubic term becomes dominant for small $\beta$ when $\gamma \approx 1$.
Note that, for $\gamma = 1$, the linear term vanishes and the cubic term 
of the velocity is $\cU(\beta) = \frac{1129}{26880}\beta^3$.
